Simulating data for the Ontario restaurant closures experiment

### 2021-02-16 outputs/paper/data_simulation.Rmd

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(kableExtra)  # for nicer tables

@@

# Sources of parameterization

# Methods of data simulation

>>>>

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(kableExtra)  # for nicer tables
library(here) # for working in projects

```{r}
all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))

all_units_data <- all_units_data %>%
  mutate(group = case_when(unit == "brant" ~ "treatment",
                           unit == "peel" ~ "treatment",
                           unit == "sudbury" ~ "treatment",
                           unit == "hamilton" ~ "control",
                           unit == "southwestern" ~ "control",
                           unit == "chatham" ~ "control"
                           ))

num_treat <- first(count(all_units_data %>%
                   filter(group == "treatment")))

num_control <- first(count(all_units_data %>%
                   filter(group == "control")))

num_total <- first(count(all_units_data))

survey_1 <- all_units_data

survey_2 <- all_units_data

@@

# Type of service provided
LORENA
## Survey 1
```{r}

## Survey 2
```{r}

# Number of employees
LALA
## Survey 1
```{r}

## Survey 2
```{r}

# Revenue

## Survey 1
```{r}

## Survey 2
```{r}

# Applications for government assistance
LORENA
## Survey 1
```{r}

## Survey 2
```{r}

# Demographic traits of owners
AMY AND LALA
## Survey 1
```{r}

## Survey 2
```{r}
